\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{listings}
\usepackage{xcolor}

\title{Summary of Spip Cleanup Feature Implementation}
\author{Gemini CLI Agent}
\date{January 30, 2026}

\begin{document}

\maketitle

\section{Overview}
A new cleanup and maintenance feature has been added to the \texttt{spip} CLI tool. This feature addresses the need for managing disk space, removing orphaned environments, and optimizing the underlying Git repositories.

\section{New Features}
\begin{itemize}
    \item \textbf{New Commands:} Added \texttt{spip gc} for maintenance and \texttt{spip matrix <pkg>} for build-server mode. \texttt{matrix} mode tests all available versions of a package for installability and functional correctness.
    \item \textbf{Matrix Mode Parallelism:} \texttt{spip matrix} now resolves all dependencies upfront and downloads all required wheels in parallel (concurrency: 4) before beginning the test execution phase.
    \item \textbf{Automatic Python Detection:} \texttt{spip matrix} now analyzes PyPI metadata to automatically determine and bootstrap the most compatible Python version for each package version.
    \item \textbf{Configuration Analysis:} Provides a detailed configuration report (matrix size, Python requirements, latest version) before starting the test suite.
    \item \textbf{Orphan Pruning:} Automatically identifies and removes environments for projects that no longer exist on the filesystem or have been unused for more than 30 days.
    \item \textbf{Automated Testing:} \texttt{spip matrix} can automatically generate robust test scripts (with fallbacks) to verify package functionality across multiple versions.
    \item \textbf{Git Optimization:} Executes rate-limited \texttt{git gc} (once every 24 hours) to maintain repository health.
\end{itemize}

\section{Implementation Details}
The implementation was performed in C++23 within \texttt{spip.cpp}. Key functions added or modified include:
\begin{itemize}
    \item \texttt{show\_usage\_stats(const Config\& cfg)}: Calculates and prints directory sizes using \texttt{std::filesystem}.
    \item \texttt{cleanup\_spip(Config\& cfg)}: Orchestrates the multi-stage cleanup process.
    \item Updated \texttt{run\_command} router to handle the new \texttt{gc} command and updated the \texttt{list} command to use detailed stats.
\end{itemize}

\section{Verification}
The feature was compiled using \texttt{g++ -std=c++23} and verified on the local system. The initial run successfully reclaimed approximately 4GB of disk space by pruning orphaned branches and compacting the Git repository.

\end{document}